---
title: "Data 605 Discussion Week 5"
author: "Yohannes Deboch"
date: "March 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1 Modify the program CoinTosses to toss a coin n times and print out after
every 100 tosses the proportion of heads minus 1/2. Do these numbers appear
to approach 0 as n increases? 
```{r}
# set.seed(1)
CoinToss <- function(n){
      headTotal <- 0
    tailTotal <- 0
for(i in 1:n){
  
    randomNumber <- runif(1,0,1)
if(randomNumber<0.5){
    outcome <- "H"
    headTotal <- headTotal + 1
}else{
    outcome <-"T"
    tailTotal <- tailTotal + 1
}
    # cat(outcome)
    if(i%%100 == 0){
        cat("Value of n: ",i," Proportions of heads:",(headTotal/i)-0.5,"\n")
 
    }
}
   cat("\n")
   print("Head ")
   print(headTotal)
   print("Tail ")
   print(tailTotal)
}
CoinToss(10000)
```
As the value of n increases the numbers approaches to 0.

 Modify the program again to print out, every
100 times, both of the following quantities: the proportion of heads minus 1/2,
and the number of heads minus half the number of tosses. Do these numbers
appear to approach 0 as n increases?
```{r}
# set.seed(1)
CoinToss <- function(n){
      headTotal <- 0
    tailTotal <- 0
for(i in 1:n){
  
    randomNumber <- runif(1,0,1)
if(randomNumber<0.5){
    outcome <- "H"
    headTotal <- headTotal + 1
}else{
    outcome <-"T"
    tailTotal <- tailTotal + 1
}
    # cat(outcome)
    if(i%%100 == 0){
        cat("Value of n: ",i," the proportion of heads minus 1/2 ",(headTotal/i)-0.5,"\n")
                cat(" the number of heads minus half the number of tosses",headTotal-i/2,"\n")

 
    }
}
   cat("\n")
   print("Head ")
   print(headTotal)
   print("Tail ")
   print(tailTotal)
}
CoinToss(10000)
```
Yes.These numbers
appears to approach 0 as n increases