---
title: "DATA 605 HW5"
author: "Yohannes Deboch"
date: "March 2, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Choose independently two numbers B and C at random from the interval [0, 1] with
uniform density. Prove that B and C are proper probability distributions.
Note that the point (B,C) is then chosen at random in the unit square.
```{r}
# Set seed v alue
set.seed(1)
n <- 1000000
# Generate two sereis of random variables B and C
B <- runif(n,0,1)
C <- runif(n,0,1)
# See first few values
head(B)
head(C)
```
To prove proper probability distributions we've to show that all all the values are greater than 0 and the empirical cumulative values lies between 0 to 1.
Here all the values of variable B and C are greater than 0.
```{r}
ecdf(B)
ecdf(C)
```
From the empirical cumulitive distribution we can see that the value of cumulutive distrubiotn functions for both B and C lies between 0 to 1 that is the total probability is 1. 

From the above discussion we can say that randomly choosen two random numbers B and C are proper probabilijty distributions.

Find the probability that
(a) B + C < 1/2.

Answer: 

We find the sum of the proabilities of each B + C < 0.5.

```{r}
sum(punif((B+C)<0.5, min=0, max=1)) / n
```
The probability that the the sum of B and C values falls below $\frac{1}{2}$ is 0.125325.
(b) BC < 1/2.

Answer: 

We find the sum of the proabilities of each B * C < 0.5.

```{r}
sum(punif((B*C)<0.5, min=0, max=1)) / n
```
The probability that the the product of B and C values falls below $\frac{1}{2}$ is 0.846724.

(c) |B − C| < 1/2.

Answer: 

We find the sum of the proabilities of each |B − C| < 1/2.
```{r}
sum(punif(abs(B-C)<0.5, min=0, max=1)) / n
```
The probability that the the absolute difference of B and C values falls below $\frac{1}{2}$ is  0.7502.

(d) max{B,C} < 1/2.

Answer: 
We find the sum of the proabilities of each max{B,C} < 1/2.
```{r}
favor <- 0
for(i in 1:length(B)){
  if(max(B[i], C[i]) < 0.5){
    favor <- favor + 1
  }
}
favor/n
```
The probability that the maximum value of B and C falls below $\frac{1}{2}$ is  0.250287.

(e) min{B,C} < 1/2.
Answer: 
We find the sum of the proabilities of each min{B,C} < 1/2.
```{r}
favor <- 0
for(i in 1:length(B)){
  if(min(B[i], C[i]) < 0.5){
    favor <- favor + 1
  }
}
favor/n
```
The probability that the minimum value of B and C falls below $\frac{1}{2}$ is  0.749991.
